Make any stupid plot you want

### 2020-12-01 draft/sections/math.tex
more on f

%%% preface w/ we care about topology & types. 
We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.

A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

then $F$ is the cross product $F= $\[T_{min}, T_{max}\]$  \times

$g(k) = (temp, time)$.  
\begin{equation}
\end{equation}

As an alternative to listing the intervals or discrete values

@@

\begin{tikzcd}
    \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
    U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
\end{tikzcd}
%%% sheaves & presheaves

>>>>

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

then $F$ is the cross product $F= \[T_{min}, T_{max}\] \times \[t_{min}, t_{max}\]$, and $g(k)$ listed in equation~\ref{eq:sigma} is:
\begin{equation}
g(k) = (x_0, x_1) \text{where} x_0 \in \[T_{min}, T_{max}\], x_1 \in \[t_{min}, t_{max}\]
\end{equation}

Given $F = X_{0} \times X_{1} \times \ldots \times X_{n}$, where $X_{0}, X_{1}, \ldots X_{n}$ are measurement spaces (e.g. ints, floats, colors).
\begin{equation}
g(k) = (x_0, x_1, \ldots x_n) \text{where} x_0 \in X_0, x_1 \in X_1, \ldots x_n \in X_n
\end{equation}

These measurement spaces $X$ are each variables and have the properties of measurement scales, such as Steven's nominal, ordinal, interval, and ratio \cite{stevensTheoryScalesMeasurement1946}

\cite{spivakSIMPLICIALDATABASES}.

@@

\begin{tikzcd}
    \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
    U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
\end{tikzcd}
